---
format: html
execute: 
  warning: FALSE
  message: FALSE
  echo: FALSE
---

```{r}
#| label: setup
library(tidyverse)
library(readr)
library(broom)
url <- "https://raw.githubusercontent.com/plotly/datasets/master/diabetes.csv"
diabetes <- read_csv(url)

cols_with_zero <- c("Glucose", "BloodPressure", "SkinThickness", "Insulin", "BMI")
diabetes[cols_with_zero] <- diabetes[cols_with_zero] |> 
  mutate(across(everything(), ~na_if(., 0)))

diabetes_clean <- diabetes |> drop_na()
```

```{r}
model <- glm(Outcome ~ ., 
             data = diabetes_clean, 
             family = binomial(link = "logit"))
```

```{r}
coef_df <- tidy(model) |> 
  filter(term != "(Intercept)") |> 
  mutate(term = fct_reorder(term, estimate))

ggplot(coef_df, aes(x = estimate, y = term)) +
  geom_point(color = "#2c7fb8", size = 3) +
  geom_errorbarh(aes(xmin = estimate - std.error*1.96, xmax = estimate + std.error*1.96), height = 0, color = "#2c7fb8") +
  labs(title = "Logistic Regression Coefficients with 95% Confidence Intervals",
       x = "Estimate",
       y = NULL) +
  theme_minimal()
```

### What This Means

This chart shows how each variable in the dataset influences the model's prediction of diabetes.

- **DiabetesPedigreeFunction** has the largest positive coefficient, meaning that patients with a stronger genetic predisposition are more likely to have diabetes — although the wide confidence interval means this result is uncertain.
- **Glucose**, **BMI**, and **Pregnancies** are meaningful predictors — as these values increase, the likelihood of diabetes also increases.
- Variables like **BloodPressure**, **Insulin**, and **SkinThickness** show little or no strong effect in this model.
- If the horizontal bar crosses the vertical line at 0, the effect of that variable isn't statistically significant.

This helps identify which health factors are most influential in predicting diabetes.

```{r}
pred_probs <- predict(model, type = "response")

ggplot(data.frame(prob = pred_probs), aes(x = prob)) +
  geom_histogram(binwidth = 0.05, fill = "#2c7fb8", color = "white") +
  labs(title = "Distribution of Predicted Diabetes Probabilities",
       x = "Predicted Probability",
       y = "Number of Patients") +
  theme_minimal()
```

### What This Means

This histogram shows how likely each patient in the dataset is predicted to have diabetes.

- Most predictions are low (under 0.3), meaning the model classifies most patients as **low-risk**.
- There’s also a clear group of patients with **high predicted probabilities** (above 0.7), meaning the model is confident that they are **likely to have diabetes**.
- The spread across the whole probability range shows that the model doesn't just guess yes or no — it gives a nuanced prediction for each person.

This distribution confirms that the model can distinguish between low-risk and high-risk individuals.
